Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Updated Paper

library(tidyverse)
```

@@

This analysis employs two predictive models to estimate the anticipated support for the two major candidates in the 2024 U.S. Presidential Election: a multiple linear regression model. These models use high-quality polling data from reputable sources, with relevant predictors to provide insights into public opinion trends.

@@

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

@@

# Additional data details

# Model details {#sec-model-details}

>>>>

library(tidyverse)
library(usmap)
library(dplyr)
library(here)
library(ggplot2)
library(janitor)
library(knitr)
library(flextable)
```

@@

This analysis employs predictive models to estimate the anticipated support for the two major candidates in the 2024 U.S. Presidential Election: a multiple linear regression model. These models use high-quality polling data from reputable sources, with relevant predictors to provide insights into public opinion trends.

@@

Predictors Selection: Variables such as sample_size, pollster, and state are included to capture systematic differences in polling methods and geographic variations in support. The date (end_date) of each poll controls for temporal effects on candidate popularity.

Linear regression was chosen for this analysis due to several key advantages. First, its simplicity and interpret ability make it highly suitable for examining the relationship between predictor variables and the response variable, specifically the candidate support percentage. Each coefficient in a linear regression model clearly represents the influence of a predictor on the outcome, which facilitates straightforward interpretation and communication of results. Moreover, linear regression is computationally efficient, making it ideal for rapid model estimation, tuning, and testing, even on relatively large datasets.

## Regression Assumptions 
- Linearity: The relationship between each predictor and the response (pct) is assumed to be linear.
- Normality: Errors are assumed to follow a normal distribution, which is tested during model diagnostics.

### Checking Assumptions

```{r}
#| tbl-cap: Checking Assumptions
#| echo: false
#| eval: true
#| warning: false
#| message: false

linear_model <- readRDS(here::here("models/linear_model.rds"))

plot(linear_model$fitted.values, residuals(linear_model), 
     main = "Residuals vs Fitted", 
     xlab = "Fitted values", 
     ylab = "Residuals")

# Q-Q Plot for Normality
qqnorm(residuals(linear_model))
qqline(residuals(linear_model))

```
In the Residuals vs. Fitted, there is no clear curved pattern, which suggests that the linear relationship might be appropriate. However, there are some clusters and a slight spread, which may indicate minor issues in capturing the relationship fully. Secondly, in the qqnorm plot, the points closely follow the diagonal line, indicating that residuals are approximately normal. This supports the normality assumption of the residuals, which is essential for reliable inference in linear regression.

## Results

@@
